---
title: "Shiny_Pitch"
author: "tinh_dexter"
date: "August 21, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
### This presentation is part of the Course Project for the Coursera Developing Data Products class. The peer assessed assignment has two parts:

#### - First, we need to create a Shiny application and deploy it on Rstudio's servers. 

#### - Second, we should use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about the application. This presentation adresses the second part of the course project. 

## What is this app about? 
### We will do these two actions:

#### - Sidebar with a slider input for number of bins

#### - Show a plot of the generated distribution

## UI codes

`library(datasets)
library(shiny)
shinyUI(fluidPage(titlePanel("Hi Shiny"),
        sidebarLayout(sidebarPanel(sliderInput("bins",
                                    "Number of bins:",
                                    min = 1,
                                    max = 500,
                                    value = 10)
                ),mainPanel(plotOutput("distPlot")
                )
        )))`

## Server codes


## Plot
```{r}
x <- faithful[, 2] 
bins <- seq(min(x), max(x))
hist(x, breaks = bins, col = 'blue', border = 'red')
```

## Thank you